Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-11-15 Article.tex
Update of Article after merge

The curves are automaticaly gotten from Gleeble system as True-stress and strain according to L-gauge where the formula to get curves are given by $\sigma =F/A\ \text{and}\ \varepsilon = \ln\left(h_0 +\Delta h / h_0\right) $or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2R_0$ and $F$ is the force as measured by Gleeble load cell.
As there are noises from raw data, filter method is applied to remove noise and have more smooth data. For further usage of  data in numerical simulation elastic parts have been removed.

@@

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:RawData}.
Almost all data are around 21030 or less than and the ammplitude of deformation is between $0.7$ and $0.85$. We have decided to limit the identification up to $0.7$ because for strain rates $2$ and $5$, stresses are note good. The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1.0~\ps$, $2.0~\ps$, and $5.0~\ps$), the flow stress increases throughout the test.
One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
For low strain rates, the effect of lubrication decreases over time and thus friction increases.
This results in a progressive increase of the flow stress.

@@

To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRV) and Dynamic Recrystallization (DRX).
At the beginning of the deformation of the sample in compression, the amount of dislocations increases and they begin to move within the material, which leads to a rapid increase in stress (strain hardening phenomenon).
As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRV. This DRV mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary. Some of these dislocations reorganize and then form sub-grains within the initial grains of the material. The combination of these dislocations moderates the increase in the number of dislocations related to work hardening and thus controls the amount of strain energy stored in the material, which influences the increase in flow stress.
The dynamic recrystallization concerns the germination of new grains, at the borders or inside the initial grains. These two phenomena explain the different shapes of the flow stress curves observed for this alloy. As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase. As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample held for $5$ minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$.
From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.

@@

The Arrhenius type model \cite{Sellars-1966} is one of the most used models in the framework of material forming, especially when it comes to studying the microstructure of the material.
Indeed, this model takes into account the physical phenomena that describe the behavior of the material in the formulation of the relationships between the stress $\sigma^y$, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ expressed as power law, exponential law and hyperbolic sine.
This makes it easier to describe the softening phenomenon observed in the material due to increasing temperature.
The following equations describe the Arrhenius model:
\begin{equation}
\mdot\varepsilon =
\begin{cases}
A_1 \sigma^{y^{n_1}} \exp{\left(-\frac{Q}{RT}\right)} & \alpha\sigma^y < 0.8\\
A_2 \exp(\beta\sigma^y) \exp{\left(-\frac{Q}{RT}\right)} & \alpha\sigma^y > 1.2\\
A_3 \left[\sinh{\left(\alpha\sigma^y\right)}\right]^{n_2} \exp{\left(-\frac{Q}{RT}\right)} & \text{for all }\sigma^y
\end{cases}
\label{eq:ArDef}
\end{equation}
with:
\begin{equation}
Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}
\end{equation}
where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha/ n_1$ are dependent of the material.
The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperature by regression method.
Combination of Equations (\ref{eq:ArDef}) and (\ref{eq:ArZ}) allow expressing the flow stress $\sigma^y$ as a function of the $Z$ parameter:
\begin{equation}
\sigma^y = \frac{1}{\alpha} \ln\left\{\left(\frac{Z}{A}\right)^{1/n} + \left[1 + \left(\frac{Z}{A}\right)^{2/n}\right]^{1/2}\right\}
\end{equation}

>>>>

\OP{Here, a part concerning the treatment of the Gleeble data is missing.
You introduce the notions of $h_0$, $R_0$, $h$, $R_M$ and $R_T$ and we have no idea what they are for.
How are the Gleeble data transformed into curves, what is the use of the previous values, what are the corrections to be made to the data,...}
The curves are automaticaly gotten from Gleeble system as True-stress and strain according to L-gauge where the formula to get curves are given by $\sigma =F/A\ \text{and}\ \varepsilon = \ln\left(h_0 +\Delta h / h_0\right) $or C-gauge whose formula are $\sigma = 4F/\pi(d+\Delta d)^2$ and $\varepsilon = 2\ln(d/(d+\Delta d))$ with $d = 2R_0$ and $F$ is the force as measured by Gleeble load cell.
As there are noises from raw data, filter method is applied to remove noise and have more smooth data.
For further usage of  data in numerical simulation elastic parts have been removed.

@@

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:RawData}.
\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...}
Almost all data are around 21030 or less than and the ammplitude of deformation is between $0.7$ and $0.85$.
We have decided to limit the identification up to $0.7$ because for strain rates $2$ and $5$, stresses are note good.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1.0~\ps$, $2.0~\ps$, and $5.0~\ps$), the flow stress increases throughout the test.
One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
For low strain rates, the effect of lubrication decreases over time and thus friction increases.
This results in a progressive increase of the flow stress.

@@

To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRV) and Dynamic Recrystallization (DRX).
At the beginning of the deformation of the sample in compression, the amount of dislocations increases and they begin to move within the material, which leads to a rapid increase in stress (strain hardening phenomenon).
As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRV.
This DRV mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary.
Some of these dislocations reorganize and then form sub-grains within the initial grains of the material.
The combination of these dislocations moderates the increase in the number of dislocations related to work hardening and thus controls the amount of strain energy stored in the material, which influences the increase in flow stress.
The dynamic recrystallization concerns the germination of new grains, at the borders or inside the initial grains.
These two phenomena explain the different shapes of the flow stress curves observed for this alloy.
As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample held for $5$ minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$.
\OP{What are the temperature and strain rate related with this micrography}
From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.

@@

The Arrhenius type model \cite{Sellars-1966} is one of the most used models in the framework of material forming, especially when it comes to studying the microstructure of the material.
Indeed, this model takes into account the physical phenomena that describe the behavior of the material in the formulation of the relationships between the stress $\sigma^y$, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ expressed as power law, exponential law and hyperbolic sine.
This makes it easier to describe the softening phenomenon observed in the material due to increasing temperature.
The following equations describe the Arrhenius model:
\begin{equation}
\mdot\varepsilon =
\begin{cases}
A_1 \sigma^{y^{n_1}} \exp{\left(-\frac{Q}{RT}\right)} & \alpha\sigma^y < 0.8\\
A_2 \exp(\beta\sigma^y) \exp{\left(-\frac{Q}{RT}\right)} & \alpha\sigma^y > 1.2\\
A_3 \left[\sinh{\left(\alpha\sigma^y\right)}\right]^{n_2} \exp{\left(-\frac{Q}{RT}\right)} & \text{for all }\sigma^y
\end{cases}
\label{eq:ArDef}
\end{equation}
with:
\begin{equation}
Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}
\end{equation}
where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $\mdot\varepsilon$ is the strain rate ($\ps$), $Q$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$), $T$ is the absolute temperature (K), $\sigma^y$ is the flow stress (MPa) for a given strain, strain rate and temperature and $A_1$, $A_2$, $A_3$, $n_1$, $n_2$, $\alpha$ and $\beta=\alpha~n_1$ are dependent of the material.
The corresponding values are independent of the temperature and are obtained from the stress-strain curves at different strain rates and temperature by regression method.
Combination of Equations (\ref{eq:ArDef}) and (\ref{eq:ArZ}) allow expressing the flow stress $\sigma^y$ as a function of the $Z$ parameter:
\begin{equation}
\sigma^y = \frac{1}{\alpha} \ln\left\{\left(\frac{Z}{A}\right)^{1/n} + \left[1 + \left(\frac{Z}{A}\right)^{2/n}\right]^{1/2}\right\}
\end{equation}
